---
title: 'Assignment 4: U.S. Senators on Twitter'
author: "YIN YI"
date: "4/16/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r Setup, include=FALSE, results='hide', warning=FALSE}
library(knitr)
opts_chunk$set(fig.path="figures/",
               cache.path="cache/",
               cache=TRUE,
               echo=TRUE,
               message=FALSE,
               warning=FALSE)  
```  

```{r load data, message=FALSE, warning=FALSE, include=FALSE}
rm(list = ls())
library(tidyverse)
```

# 1. Who follows whom?
## a) Network of Followers

```{r, message=FALSE}
links<-read_csv("senators_follow.csv")%>%
        select(source, target, following)%>%
        filter(following=='TRUE')%>%select(-following)%>%
        rename(from = source, to = target)

nodes <-read_csv("senators_twitter.csv")%>%
        select(`Official Twitter`, 
                         Senator,
                         State,
                         `Party affiliation`,
                         label)%>%
        rename( id = `Official Twitter`,
                party = `Party affiliation`,
                name = Senator,
                state = State)
        
links <-links%>%filter(from %in% nodes$id)%>%
        filter(to %in% nodes$id)
```

Create a directed network graph.
```{r}
library("igraph")
net <- graph_from_data_frame(d=links, vertices=nodes, directed=T)
```

### the highest “in-degree”
Identify the three senators who are followed by the most of their colleagues
```{r top indegree}
nodes$indegree<-degree(net, mode = "in",normalized = T)
nodes%>%select(name, indegree)%>%arrange(desc(indegree))%>%top_n(3)
```

```{r graph configure}
nodes<-nodes%>%
        mutate(pcolor = case_when(party =="Democratic Party" ~ "#58A5D4",
                                  party =="Independent" ~ "#D9A6DF",
                                  party =="Republican Party" ~"#DB3F3F"))


E(net)$width <- 0.1
E(net)$edge.color <- "#7F7F7F1A"
V(net)$label.family <-"Palatino"
V(net)$label.color <-"#292527"
V(net)$color <- nodes$pcolor
```


```{r fig.align="center", fig.height=11, fig.width=13,results='hide'}
nodes<-nodes%>%mutate(topin = ifelse(indegree>=0.89,
                                     str_remove(label,"\\s\\([R|D]\\)"),
                                     NA))
V(net)$label <- nodes$topin
V(net)$label.cex <- 1
V(net)$label.degree<-pi/3
V(net)$label.dist <-0.5
V(net)$size <- nodes$indegree*5
E(net)$arrow.size <- 0.4

tex <- "(blue = Democrat, red = Republican, purple = independent)\n(size: Indegree centrality)"


plot(net, layout=layout_with_kk(net))+
        title("Having Followers",sub = tex, 
   font.sub = 3, 
   font.main = 2,
   cex.main = 1.5,
   cex.sub= 1)
```

### the highest “out-degree”

the three senators who follow the most of their colleagues 
```{r}
nodes$outdegree<-igraph::degree(net, mode = "out",normalized = T)
nodes%>%select(name, outdegree)%>%arrange(desc(outdegree))%>%
        .[0:3,]

```

### the highest “out-degree”
```{r fig.align="center", fig.height=11, fig.width=13,results='hide'}
nodes<-nodes%>%mutate(topout = ifelse(outdegree>=0.74, 
                                      str_remove(label,"\\s\\([R|D]\\)"),
                                      NA))
V(net)$label <- nodes$topout
V(net)$label.cex <- 1
V(net)$label.degree<-pi/3
V(net)$label.dist <-0.5
V(net)$size <- nodes$outdegree*5
E(net)$arrow.size <- 0.4


tex <- "(blue = Democrat, red = Republican, purple = independent)\n(size: Outdegree centrality)"

plot(net, layout=layout_with_kk(net))+
        title("Following", sub = tex, 
   font.sub = 3, 
   font.main = 2,
   cex.main = 1.5,
   cex.sub= 1)
```

### the highest “centrality”
(blue = Democrat, red = Republican, purple = independent) 
(size: Eigenvector centrality)
```{r}
nodes$central<-eigen_centrality(net, directed = TRUE, scale = TRUE,weights = NULL, options = arpack_defaults)$vector
nodes%>%select(name,central)%>%arrange(desc(central))%>%
        .[0:3,]

```

```{r, fig.height=11, fig.width=13, results='hide'}

nodes<-nodes%>%mutate(topcent = ifelse(central>=0.98, 
                                      str_remove(label,"\\s\\([R|D]\\)"),
                                     NA))
V(net)$label <- nodes$topcent
V(net)$label.cex <- 1
V(net)$label.degree<-pi/3
V(net)$label.dist <-0.5
V(net)$size <- nodes$central*5
E(net)$arrow.size <- 0.4

tex <- "(blue = Democrat, red = Republican, purple = independent)\n(size: Eigenvector centrality)"
plot(net, layout=layout_with_kk(net))+
        title("Eigenvector Centrality",sub = tex, 
   font.sub = 3, 
   font.main = 2,
   cex.main = 1.5,
   cex.sub= 1)
```




## b) Communities
Community detection result is similer to party identification.
```{r}

wc <- cluster_walktrap(net)  # find "communities"
members <- membership(wc)
# library(RColorBrewer)
mcol <-RColorBrewer::brewer.pal(8, "Pastel1")


```


```{r,fig.height=10, fig.width=20, message=FALSE, warning=FALSE, results='hide'}
par(mfrow=c(1,2))
E(net)$edge.color <- "#7F7F7F66"
E(net)$arrow.size <- 0.1
E(net)$width <- 0.3
V(net)$label <- NA
V(net)$size <- 5
V(net)$color <- mcol[members]
tex <- "Color of Node: Community Cluster"
plot(net,layout=layout_with_kk(net))+
        title("Community Detection",
              sub = tex, 
              font.sub = 3, 
                font.main = 2,
                cex.main = 2,
                cex.sub= 1)


V(net)$size <- 5
V(net)$color <- nodes$pcolor
tex <- "(blue = Democrat, red = Republican, purple = independent)"
plot(net,layout=layout_with_kk(net))+title("Party Identification",          
                                           sub = tex, font.sub = 3, 
                                           font.main = 2,cex.main = 2,
                                           cex.sub= 1)
dev.off()
```

# 2. What are they tweeting about?

## a) Most Common Topics over Time
```{r, results='hide'}
rm(list = ls())
library(tidyverse)
# Read in the Tweets
senator_tweets <- readRDS("senator_tweets.RDS")

hashtags <- senator_tweets%>%filter(is_retweet==FALSE)%>%
        select(hashtags)%>%
        filter(is.na(hashtags)==FALSE)%>%
        mutate(id = row_number())

topic<-unnest(hashtags)
```


```{r, results='hide', fig.align='center', fig.height=4, fig.width=7}
topic%>%group_by(hashtags)%>%
        summarise(freq = n())%>%
        arrange(desc(freq))%>%
        top_n(10)%>%
        ggplot(aes(y= freq, x=reorder(hashtags, freq)))+
        geom_bar(stat = "identity", aes(fill = hashtags))+coord_flip()+
        scale_fill_brewer(palette = "Set3") + 
        labs(title = "Most Popular Topic (Top 10 Hashtags)",
             x="", y="")+
        theme_bw(base_size = 12, base_family = "Palatino")+
        theme(plot.title = element_text(hjust = 0.5),legend.position = "none")

```


## b) Russia investigation - Dems vs. Reps
The subset of senator tweets that included these hashtags ,
```{r}
rm(hashtags)

ru<-senator_tweets%>%
        filter(is_retweet==FALSE)%>%
        filter(is.na(hashtags)==FALSE)%>%
        select(screen_name, text)%>%
        mutate(id = row_number())%>%full_join(topic)


ru_inve<-ru%>%filter(str_detect(hashtags, "[M|m]ueller")==T|
                     str_detect(hashtags, "[R|r]ussia")==T|
                   str_detect(hashtags, "[I|i]nvestigation")==T|
                str_detect(hashtags, "[C|c]ollusion")==T|
                 str_detect(hashtags, "[H|h]illary")==T)
```
Show whether and how senators from different parties talk differently about the issue of the special counsel investigation.

```{r,results='hide'}
pid <-read_csv("senators_twitter.csv")%>%
        select(`Official Twitter`, 
                         `Party affiliation`)%>%
        rename( screen_name = `Official Twitter`,
                party = `Party affiliation`)

ru_inve<-ru_inve%>%left_join(pid)
```

```{r, results='hide', echo=FALSE}
hash_words<-"([M|m]ueller|[R|r]ussia|[I|i]nvestigation|[C|c]ollusion|[H|h]illary|[T|t]rump)"

sucdf <-ru_inve%>%select(text, party)%>%
        filter(party %in% c("Democratic Party", "Republican Party"))%>%
        group_by(party)%>%
        summarise(text = paste0(text, collapse = "\n"))%>%
        mutate(doc_id = row_number())%>%
        select(doc_id,text, party)%>%
        mutate(text = str_remove_all(text, hash_words))

library(tm)
# function to clean the text
removeFullCap <- function(x){gsub("\\b[A-Z]+\\b", "", x)}
removeNumPunct <- function(x){gsub("[^[:alpha:][:space:]]*", "", x)}

clean_corpus <- function(corpus){
  corpus <-corpus%>%tm_map(content_transformer(removeFullCap))%>%
          tm_map(content_transformer(tolower))%>%
          tm_map(removeWords, c(stopwords("en")))%>%
          tm_map(removeNumbers)%>%
          tm_map(content_transformer(removeNumPunct))%>%
          tm_map(stripWhitespace)
  return(corpus)
}

# cleaned text corpus
suc_clean <- sucdf%>%
        DataframeSource()%>%
        VCorpus()%>%
        clean_corpus()

library(SnowballC)    
# stem words
suc_stemmed <- tm_map(suc_clean, stemDocument)

# the following stem completion works in tm v0.6 
comp_suc <-tm_map(suc_stemmed, 
                      content_transformer(function(x, d)
                      paste(stemCompletion(strsplit(stemDocument(x), ' ')[[1]], d),collapse = ' ')), suc_clean)


# document-term-matrix.
suc_tdm <-TermDocumentMatrix(comp_suc) 

# Convert the Term-Document-Matrix
all_m <- as.matrix(suc_tdm)

# Create common_words
common_words <- subset(all_m, all_m[, 1] > 0 & all_m[, 2] > 0)

# Create difference
difference <- abs(common_words[, 1] - common_words[, 2])

# Combine common_words and difference
common_words <- cbind(common_words, difference)

# Order the data frame from most differences to least
common_words <- common_words[order(common_words[, 3], decreasing = TRUE), ]


```

```{r, message=FALSE, warning=FALSE, fig.align='center'}

# Create top25_df
top25_df <- data.frame(x = common_words[1:25, 1], 
                       y = common_words[1:25, 2], 
                       labels = rownames(common_words[1:25, ]))

top25 <- top25_df
colnames(top25) = c("Democratic", "Republican","terms")
top25 <- top25 %>% gather(Party, Frequency, -terms)

top25$Frequency <- ifelse(top25$Party=="Republican",
                          top25$Frequency,top25$Frequency*-1)


ggplot(top25, aes(x = reorder(terms, Frequency), 
                  y = Frequency, fill = Party)) +
  geom_bar(data = filter(top25, Party == "Democratic"), stat = "identity") +  
  geom_bar(data = filter(top25, Party == "Republican"), stat = "identity") + 
  scale_fill_brewer(palette = "Set1", direction=-1) + coord_flip() + 
        labs(x = " ", y = " ")+
  scale_y_continuous(breaks = seq(-50, 50, 25)) + ylab("") +
  theme_bw()+theme(legend.justification=c(1,1), legend.position=c(1,1)) 
```

```{r, results='hide', echo=FALSE}
rm(list = c('all_m', 'common_words', 'comp_suc', 'ru_inve', 'suc_clean',
     'suc_stemmed','suc_tdm','sucdf', 'top25', 'top25_df','difference'))
```

## c) Russia investigation - Barr report
```{r}
library(lubridate)
library(tidytext)
bar_w <-'([B|b]arr)|([R|r]eport)|([S|s]ummary)|(AG)|(Attorney General)|(Mueller)'

barr<-senator_tweets %>% 
  filter(created_at >= as.Date("2019-03-24"))%>%
        filter(is_retweet==FALSE)%>%
        filter(str_detect(text, "([B|b]arr)")==T)%>%
        filter(str_detect(text, "([R|r]eport)|([S|s]ummary)")==T)%>%
        select(screen_name, text)%>%
        group_by(screen_name)%>%
        summarise(text = paste0(text, collapse = "\n"))%>%
        mutate(doc_id = row_number())%>%
        select(doc_id,text, screen_name)%>%
        mutate(text = str_remove_all(text, bar_w))
      

# cleaned text corpus
barr_clean <- barr%>%
        DataframeSource()%>%
        VCorpus()%>%
        clean_corpus()

barr_stemmed <- tm_map(barr_clean, stemDocument)

# the following stem completion works in tm v0.6 
barr_comp <-tm_map(barr_stemmed , 
                      content_transformer(function(x, d)
                      paste(stemCompletion(strsplit(stemDocument(x), ' ')[[1]], d),
                      collapse = ' ')), barr_clean)

barr_dtm <-DocumentTermMatrix(barr_comp)  

barr_np<-tidy(barr_dtm)%>%rename(word = term)%>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  reshape2::acast(word ~ sentiment, value.var = "n", fill = 0) 
```


```{r, fig.align='center', fig.width=6, fig.height=6}
library(wordcloud)
set.seed(9102)
barr_np%>%comparison.cloud(colors = c("#5ab4ac", "#e9a3c9"),
                   max.words = 2000)
```

```{r, echo=FALSE}
rm(barr, barr_clean, barr_comp, barr_dtm, barr_np, 
            barr_stemmed, bar_pattern, bar_sum, bar_w,
            hash_words)
```


# 3. Are you talking to me?

## a) Identifying Re-Tweets

Select the set of re-tweeted messages from other senators and identify the source of the originating message. 

Calculate by senator the amount of re-tweets they received and from which party these re-tweets came. 
```{r, echo=FALSE}
retw<-senator_tweets %>% 
        filter(is_retweet==TRUE)%>%
        select(text, screen_name)%>%
        mutate(source = str_extract(text,"(?<=(RT\\s@))([^:]*)(?=:\\s)"))%>%
        filter(source %in% screen_name)%>%
        select(-text)

wre<-retw%>%filter(screen_name!=source)%>%
        group_by(screen_name, source)%>%
        summarise(weight=n())%>%
        ungroup()%>%mutate(screen_name=tolower(screen_name),
                           source = tolower(source))

sid<-pid%>%mutate(screen_name= tolower(screen_name))


wre<-wre%>%left_join(sid)%>%rename(from_p = party)

sid<-sid%>%rename(source = screen_name)

wre<-wre%>%left_join(sid)%>%rename(to_p = party)

wre<-wre%>%mutate(type=ifelse(from_p==to_p, "Same", "Different"))

relinks<- wre%>%rename(from = screen_name,
                  to = source)%>%
        select(from, to, weight, type)

renodes <-read_csv("senators_twitter.csv")%>%
        mutate(id = tolower(`Official Twitter`))%>%
        select(id, Senator,`Party affiliation`,label)%>%
        rename(party = `Party affiliation`,
                name = Senator)


library("igraph")
regraph <- graph_from_data_frame(d=relinks, vertices=renodes, directed=T)

renodes<-renodes%>%
        mutate(pcolor = case_when(party =="Democratic Party" ~ "#58A5D4",
                                  party =="Independent" ~ "#D9A6DF",
                                  party =="Republican Party" ~"#DB3F3F"))

```


visualize whether senators largely re-tweet their own party colleagues’ messages:

Most retweets happens between members from the same party, but for those who receive large amount retweets would get retweeted from senators from different party. As expected, Independents receive and retweet senators in different parties mostly.


```{r,fig.height=13, fig.width=13, results='hide'}
adjustcolor("gray50", alpha=.4)
tcol<-c("#FFA500B3", "#7F7F7F4D")
E(regraph)$color <- tcol[as.factor(E(regraph)$type)]
# E(regraph)$color[E(regraph)$type == "Different"] <- 'red'
# E(regraph)$color[E(regraph)$type == "Different"] <- 'gray80'
E(regraph)$arrow.size <- 0.8
E(regraph)$width <- E(regraph)$weight/2
V(regraph)$size <- 5
V(regraph)$label <- NA
V(regraph)$label.family <-"Palatino"
V(regraph)$color <- renodes$pcolor

tex <- "Orange edge means retweet from member in different party\nWidth of edge is the times of retweets from another node"
plot(regraph, layout=layout_with_kk(regraph))+
        title(main = "Retweet Network", 
   sub = tex, 
   font.sub = 3, 
   font.main = 2,
   cex.main = 1.5,
   cex.sub= 1)
```

### b) Identifying Mentions

Convert the information to an undirected graph object in which the number of mentions is the strength of the relationship between senators.


```{r, echo=FALSE}

mention<-senator_tweets %>% 
        filter(is_retweet==FALSE)%>%
        filter(is.na(hashtags)==FALSE)%>%
        select(screen_name, mentions_screen_name)

mention<-mention%>%unnest()%>%
        filter(tolower(mentions_screen_name) %in% tolower(screen_name))

mention<-mention%>%
        group_by(screen_name, mentions_screen_name)%>%
        summarise(weight=n())%>%
        ungroup()%>%mutate(from=tolower(screen_name),
                           to = tolower(mentions_screen_name))


mlinks<- mention%>%select(from, to, weight)%>%filter(to!=from)

mnodes <-read_csv("senators_twitter.csv")%>%
        mutate(id = tolower(`Official Twitter`))%>%
        select(id, `Party affiliation`)%>%
        rename(party = `Party affiliation`)


library("igraph")
mgraph <- graph_from_data_frame(d=mlinks, vertices=mnodes, directed=F)
```


Comment on what you can see from the visualization:

The most frequent mentions are happen between senators from the same party.
```{r,fig.height=13, fig.width=13, results='hide'}
mnodes<-mnodes%>%
        mutate(pcolor = case_when(party =="Democratic Party" ~ "#58A5D4",
                                  party =="Independent" ~ "#D9A6DF",
                                  party =="Republican Party" ~"#DB3F3F"))

mnodes$indegree<-degree(mgraph, mode = "in",normalized = T)

E(mgraph)$color <- "#7F7F7F4D"
E(mgraph)$arrow.size <- 0.8
E(mgraph)$width <- E(mgraph)$weight/2
V(mgraph)$size <- mnodes$indegree*5
V(mgraph)$label <- NA
V(mgraph)$color <- mnodes$pcolor

tex <- "blue=Democrats,red=Republicans\nsize:times of mention (normalized)"
plot(mgraph, layout=layout_with_kk(mgraph))+
        title(main = "Mention Network", 
   sub = tex, 
   font.sub = 3, 
   font.main = 2,
   cex.main = 1.5,
   cex.sub= 1)

```

