---
title: 'Assignment 3: Kickstarter Projects'
author: "YIN YI"
date: "4/4/2019"
output: html_document
---

```{r Setup, include=FALSE, results='hide', warning=FALSE}
library(knitr)
opts_chunk$set(fig.path="figures/",
               cache.path="cache/",
               cache=TRUE,
               echo=TRUE,
               message=FALSE,
               warning=FALSE)  
```  

# 1. Identifying Successful Projects

```{r, message=FALSE, warning=FALSE, results='hide', fig.width=12, fig.height=5}
library(tidyverse)
projects <- read_csv("kickstarter_projects.csv")

projects%>%
        select(state, top_category, id)%>%
        group_by(top_category,state)%>%
        summarise(n= n())%>%
        group_by(top_category)%>%
        mutate(proportion = n/sum(n))%>%
        ggplot( aes(x = top_category, 
                    y = proportion, 
                    fill = state)) + 
        geom_bar(stat = "identity")+ 
        labs(x = "Categories", y = "Proportion")+
        ggtitle("State by Project Category")+
        theme_bw(base_family = "Palatino", base_size = 13)+
        theme(plot.title = element_text(hjust=0.5))
        
```

# 2. Writing your success story

## a) Cleaning the Text and Word Cloud

select the 1000 most successful projects and a sample of 1000 unsuccessful projects.
```{r}
set.seed(9102)
textdf<-projects%>%
        select(blurb, state)%>%
        mutate(suc = ifelse(state == "successful", 1, 0))%>%
        group_by(suc)%>%sample_n(1000)%>%ungroup()%>%
        select(blurb, suc)%>%rename(text = blurb)%>%
        mutate(doc_id = row_number())%>%
        select(doc_id,text, suc)%>%data.frame(stringsAsFactors = F)
```

remove unnecessary words (stop words), syntax, punctuation, numbers, white space etc. 
```{r, message=FALSE, warning=FALSE}
library(tm)
# function to clean the text
removeFullCap <- function(x){gsub("\\b[A-Z]+\\b", "", x)}
removeNumPunct <- function(x){gsub("[^[:alpha:][:space:]]*", "", x)}

clean_corpus <- function(corpus){
  corpus <-corpus%>%tm_map(content_transformer(removeFullCap))%>%
          tm_map(content_transformer(tolower))%>%
          tm_map(removeWords, c(stopwords("en")))%>%
          tm_map(removeNumbers)%>%
          tm_map(content_transformer(removeNumPunct))%>%
          tm_map(stripWhitespace)
  return(corpus)
}

# cleaned text corpus
kick_clean <- textdf%>%
        DataframeSource()%>%
        VCorpus()%>%
        clean_corpus()
```

Stem the words left over and complete the stems.
```{r, message=FALSE, warning=FALSE}
library(SnowballC)    
# stem words
kick_stemmed <- tm_map(kick_clean, stemDocument)


# the following stem completion works in tm v0.6 
comp_stemmed <-tm_map(kick_stemmed, 
                      content_transformer(function(x, d)
                      paste(stemCompletion(strsplit(stemDocument(x), ' ')[[1]], d),
                      collapse = ' ')), kick_clean)

```


Create a document-term-matrix.
```{r}
# document-term-matrix.
kick_dtm <-DocumentTermMatrix(comp_stemmed)  

```


calculate ti-idf
```{r, message=FALSE, warning=FALSE}
library(tidytext)
# tidy object
kick_dt <- tidy(kick_dtm)
meta <-textdf%>%select(doc_id, suc)%>%rename(document = doc_id)


kick <- kick_dt%>%mutate(document = as.integer(document))%>%
        left_join(meta)%>%
        mutate(success = ifelse(suc == 1, "Successful", "Not Successful"))%>%
        select(-suc)


kick_tf_idf <-  kick%>%
                bind_tf_idf(term, document, count)
```

Provide a word cloud of term frequnecy
```{r, message=FALSE, warning=FALSE,fig.width=9, fig.height=9}

term_frequency_DT <- kick_tf_idf

library(wordcloud)

set.seed(9102)


RdBu<- RColorBrewer::brewer.pal(10, "RdBu")


wordcloud(term_frequency_DT$term,
          term_frequency_DT$tf, 
         max.words = 100, colors = RdBu)
```




## b) Success in words

```{r, message=FALSE, warning=FALSE, results='hide', echo=FALSE}

set.seed(9102)

sucdf<-projects%>%
        select(blurb, state)%>%
        mutate(suc = ifelse(state == "successful", 1, 0))%>%
        group_by(suc)%>%sample_n(1000)%>% 
        summarise(text = paste0(blurb, collapse = "\n"))%>%
        mutate(doc_id = row_number())%>%
        select(doc_id,text, suc)%>%data.frame(stringsAsFactors = F)


suc_clean <- sucdf%>%
        DataframeSource()%>%
        VCorpus()%>%
        clean_corpus()

# stem words
suc_stemmed <- tm_map(suc_clean, stemDocument)

# the following stem completion works in tm v0.6 
comp_suc <-tm_map(suc_stemmed, 
                      content_transformer(function(x, d)
                      paste(stemCompletion(strsplit(stemDocument(x), ' ')[[1]], d),collapse = ' ')), suc_clean)


# document-term-matrix.
suc_tdm <-TermDocumentMatrix(comp_suc) 

# Convert the Term-Document-Matrix
all_m <- as.matrix(suc_tdm)

# Create common_words
common_words <- subset(all_m, all_m[, 1] > 0 & all_m[, 2] > 0)

# Create difference
difference <- abs(common_words[, 1] - common_words[, 2])

# Combine common_words and difference
common_words <- cbind(common_words, difference)

# Order the data frame from most differences to least
common_words <- common_words[order(common_words[, 3], decreasing = TRUE), ]
```

```{r, message=FALSE, warning=FALSE}

# Create top25_df
top25_df <- data.frame(x = common_words[1:25, 1], 
                       y = common_words[1:25, 2], 
                       labels = rownames(common_words[1:25, ]))

top25 <- top25_df
colnames(top25) = c("Unsuccessful", "Successful","terms")
top25 <- top25 %>% gather(Success, Frequency, -terms)

top25$Frequency <- ifelse(top25$Success=="Successful",
                          top25$Frequency,top25$Frequency*-1)


ggplot(top25, aes(x = reorder(terms, Frequency), 
                  y = Frequency, fill = Success)) +
  geom_bar(data = filter(top25, Success == "Unsuccessful"), stat = "identity") +  
  geom_bar(data = filter(top25, Success == "Successful"), stat = "identity") + 
  scale_fill_brewer(palette = "Set1", direction=1) + coord_flip() + 
        labs(x = " ", y = " ")+
  scale_y_continuous(breaks = seq(-50, 50, 25)) + ylab("") +
  theme_bw()+theme(legend.justification=c(1,1), legend.position=c(1,1)) 
```

## c) Simplicity as a virtue

Calculate a readability measure 
```{r}
require(quanteda)
require(dplyr)

quant_corpus<-corpus(textdf)
FRE_kick <- textstat_readability(quant_corpus,
              measure=c('Flesch.Kincaid'))

readbility <-FRE_kick%>%
        mutate(doc_id =as.integer(document))%>%
        select(doc_id, Flesch.Kincaid)%>%left_join(textdf)%>%
        mutate(success = ifelse(suc ==1, "Successful", "Not Successful"))%>%
        select(doc_id, success, Flesch.Kincaid)%>%
        mutate(success = as.factor(success))
```

Visualize the relationship between the readability measure and one of the measures of success. Briefly comment on your finding.

--**There is no significant difference of readability between successful and unsuccessful groups**

```{r, fig.width=5, fig.height=5}
ggplot(readbility, aes(x=success, y=Flesch.Kincaid)) + 
  geom_boxplot(notch=TRUE)+ 
        stat_summary(fun.y=mean, geom="point", shape=23, size=4)+
        scale_fill_brewer(palette="Blues")+
        ggtitle("Readability by Result")+
        theme_classic(base_family = "Palatino")+
        theme(plot.title = element_text(hjust=0.5))
```

# 3. Sentiment
## a) Stay positive
Visualize the relationship between tone of the document and success. Briefly comment.

--**There is no significant difference of sentiment between successful and unsuccessful groups**

```{r, fig.width=5, fig.height=5}
library(tidytext)
sentiment <- function(words){
  require(quanteda)
  tok <- quanteda::tokens(words)
  pos.count <- sum(tok[[1]]%in%pos[,1])
  neg.count <- sum(tok[[1]]%in%neg[,1])
  sent_score <- (pos.count - neg.count)
  return(sent_score)
}

suc_dt <- tidy(suc_tdm)%>%
        mutate(success = ifelse(document =="1", "Unsuccessful", 
                                                  "Successful"))%>%
        rename(word = term)%>%
         inner_join(get_sentiments("afinn"))%>%
        mutate(success = as.factor(success)) 

ggplot(suc_dt, aes(x=success, y=score)) + 
  geom_boxplot(notch=TRUE)+ 
        stat_summary(fun.y=mean, geom="point", shape=23, size=4)+
        scale_fill_brewer(palette="Blues")+
        ggtitle("Sentiment Score by Result")+
        theme_classic(base_family = "Palatino")+
        theme(plot.title = element_text(hjust=0.5))

```

## b) Positive vs negative

Generate a comparison cloud showing the most-frequent positive and negative words.

```{r, message=FALSE, warning=FALSE, fig.width=8, fig.height=8}
require(reshape2)
library(wordcloud)

com_df<-tidy(suc_tdm)%>%rename(word = term)%>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  reshape2::acast(word ~ sentiment, value.var = "n", fill = 0) 

set.seed(9102)
com_df%>%comparison.cloud(colors = c("#8c510a", "#01665e"),
                   max.words = 2000)

```

## c) Get in their mind
```{r}
unsuc_nrc_df<-tidy(suc_tdm)%>%filter(document =="1")%>%
        rename(word = term)%>%
  inner_join(get_sentiments("nrc")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0)

suc_nrc_df<-tidy(suc_tdm)%>%filter(document =="2")%>%
        rename(word = term)%>%
  inner_join(get_sentiments("nrc")) %>%
  count(word, sentiment, sort = TRUE) %>%
  acast(word ~ sentiment, value.var = "n", fill = 0)



Paired <- RColorBrewer::brewer.pal(10, "Paired")
```

## Unsuccessful 
```{r, fig.width=10, fig.height=10}
set.seed(9102)
unsuc_nrc_df%>%comparison.cloud(colors = Paired,
                   max.words = 5000)
```

## Successful 
```{r, fig.width=10, fig.height=10}
suc_nrc_df%>%comparison.cloud(colors = Paired,
                   max.words = 5000)

```

             