---
title: "Geographical Mapping: Parking Violations in NYC"
author: "YI YIN"
date: 2019-02-24
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
editor_options: 
  chunk_output_type: console
---
# Scope
- Data exploration
- Choropleth maps 
- Use geo-coding API to locate address for mapping
- Interactive map with hover-over information
- Interactive map with clustering

```{r Setup, include=FALSE, results='hide', warning=FALSE}
library(knitr)
opts_chunk$set(fig.path="figures/",
               cache.path="cache/",
               cache=TRUE,
               echo=FALSE,
               message=FALSE,
               warning=FALSE)  
```  

```{r package, include=TRUE, results='hide', warning=FALSE}
library(tidyverse)
```

# Data exploration

## a) Violation Code and Fine Amounts
```{r read_data, include=TRUE, results='hide', warning=FALSE}
# load data into space
parking <-read_csv("parking/parkingNYC_Jan2019.csv")
vio_code <- readxl::read_xlsx("parking/parkingNYC_ParkingViolationCodes_Nov_2018.xlsx")

# rename variable names
colnames(parking)<-stringr::str_replace_all(colnames(parking), " ", "_" )%>%
        stringr::str_to_lower()
colnames(vio_code)<-stringr::str_replace_all(colnames(vio_code), " ", "_" )%>%
        stringr::str_to_lower()

colnames(parking)[5] <-"issue_date_chr"

vio_code <-vio_code%>%
        rename(fine_amount_b96=`manhattan__96th_st._&_below\r\n(fine_amount_$)`)%>%
        rename(fine_amount_other = `all_other_areas\r\n(fine_amount_$)`)
```

```{r }
# Add the violation code descriptions and fine amounts to the data file. 
data <- left_join(parking, vio_code, by="violation_code")


data <-data%>%select(-`violation_description.x`)%>%
        rename(violation_description=`violation_description.y`)
```

Provide a visual overview of the top 10 most common types of violations 
```{r}

vio_type <- data%>%
        select(violation_description)%>%
        group_by(violation_description)%>%
        summarise(count = n())

vio_type%>%
        top_n(10, count)%>%
        ggplot(aes(y= count, x=reorder(violation_description, count)))+
        geom_bar(stat = "identity")+coord_flip()+
        labs(title = "Top 10 Most Common Types of Violations",
             x="", y="")+
        theme_bw(base_size = 12, base_family = "Palatino")+
        theme(plot.title = element_text(hjust = 0.5))

```

Compare how this ranking differs if we focus on the total amount of revenue generated.
```{r}
revenue <- data%>%
        select(violation_description, fine_amount_other)%>%
        group_by(violation_description)%>%
        summarise(rev = sum(fine_amount_other))

revenue%>%
        top_n(10, rev)%>%
        ggplot(aes(y= rev, x=reorder(violation_description, rev)))+
        geom_bar(stat = "identity")+coord_flip()+
        labs(title = "Total Amount of Revenue Generated ($)",
             x="", y="")+ 
        theme_bw(base_size = 12, base_family = "Palatino")+
        theme(plot.title = element_text(hjust = 0.5))

```

## b) Average amount of fine by vehicle
Compare the average amount of fine by vehicle color, vehicle year, and vehicle plate type.

```{r}
# plate_type
data%>%filter(plate_type %in% c("COM","PAS"))%>%
        select(plate_type, fine_amount_other)%>%
        group_by(plate_type)%>%
        summarise(avg = sum(fine_amount_other, na.rm = T)/n())
# vehicle_color
data%>%select(vehicle_color, fine_amount_other)%>%
        group_by(vehicle_color)%>%
        summarise(avg = sum(fine_amount_other, na.rm = T)/n())%>%
        arrange(desc(avg))

# vehicle_year
data%>%select(vehicle_year, fine_amount_other)%>%
        group_by(vehicle_year)%>%
        summarise(avg = sum(fine_amount_other, na.rm = T)/n())%>%
        arrange(desc(avg))


```


```{r include=FALSE, results='hide', warning=FALSE}
rm(avg_fine_color)
rm(avg_fine_type)
rm(avg_fine_year)
rm(parking)
rm(revenue)
rm(vio_code)
rm(vio_type)

```

# Choropleth maps 

Map by Precincts: Read in the shape files for the police precincts and remove all precincts outside of Manhattan.
```{r, warning=FALSE, message=FALSE}
library(rgdal)
library(sp)
nypp <-readOGR("police_precincts/.","nypp")
# remove all precincts outside of Manhattan.
nypp_m <- subset(nypp, nypp@data$Precinct%in%c(1:39))

rm(nypp)

```

## a) Number of tickets, total fines, and average fines
Provide three maps that show choropleth maps of:

```{r warning=FALSE, message=FALSE}
library(tmap)
layout <- tm_layout(  
          legend.title.size = 1,
          legend.text.size = 0.6,
          legend.position = c(0.8,0),
          legend.bg.color = "white",
          legend.bg.alpha = 1,
          bg.color="white",
          frame=FALSE)

ticket <- data%>%
        select(violation_code, violation_precinct)%>%
        rename(Precinct=violation_precinct)%>%
        filter(Precinct<40)%>%
        group_by(Precinct)%>%
        summarise(ticket_n = n())

ny_ti <-sp::merge(nypp_m, ticket, by = "Precinct")

palb <- RColorBrewer::brewer.pal(6,'GnBu')
tm1<-tm_shape(ny_ti) + layout +
        tm_borders()+
        tm_fill("ticket_n", palette=palb,
                title = "Total Number of Tickets by Precinct") 

```



```{r}
total<-data%>%select(fine_amount_other, violation_precinct)%>%
        rename(Precinct=violation_precinct)%>%
        filter(Precinct<40)%>%
        group_by(Precinct)%>%
        summarise(total_amount = sum(fine_amount_other, na.rm = T))

ny_total <-sp::merge(nypp_m, total, by = "Precinct")

palp <- RColorBrewer::brewer.pal(6,'RdPu')

tm2<-tm_shape(ny_total) + layout +
        tm_borders()+
        tm_fill("total_amount", palette=palp,
                title = "Total Amount of Fines by Precinct") 


```

```{r}

avg_f<-data%>%select(fine_amount_other,
                     violation_precinct)%>%
        rename(Precinct=violation_precinct)%>%
        filter(Precinct<40)%>%
        group_by(Precinct)%>%
        summarise(avg_amount = sum(fine_amount_other, na.rm = T)/n())

ny_avg <-sp::merge(nypp_m, avg_f, by = "Precinct")

paly <- RColorBrewer::brewer.pal(6,'YlOrBr')

tm3<-tm_shape(ny_avg) + layout +
        tm_borders()+
        tm_fill("avg_amount", palette=paly,
                title = "Average Amount of Fines by Precinct") 
```

### The Total Number of Tickets

```{r}
tm1

```

### The Total Amount of Fines
```{r}

tm2

```

### The Average Amount of Fines
```{r}

tm3
```

Upper east side has the highest total number of tickets, and total amount of fines. While Midtown has the highest average amount of fines.


## b) Types of violations
Group the almost 100 types of ticket violations into a smaller set of 4-6 subgroups.

A Choropleth maps for each of these subgroups to show where different types of violations are more or less common.

```{r}
viogroup <- data%>%select(violation_description,violation_precinct)

library(stringr)
viogroup$newg <-case_when(str_detect(viogroup$violation_description, 
                                              "NO STAND") ~ "NO_STAND",
                          str_detect(viogroup$violation_description, 
                                              "NO PARKING") ~ "NO PARKING",
                          str_detect(viogroup$violation_description, 
                                              "MISSING") ~ "MISSING",
                          str_detect(viogroup$violation_description, 
                                              "FAIL TO") ~ "FAIL TO",
                          TRUE ~ "Other")


```

```{r}

FAIL<-viogroup%>%
        rename(Precinct=violation_precinct)%>%
        filter(Precinct<40, newg =="FAIL TO")%>%
        group_by(Precinct)%>%
        summarise(tot = n())

ny_FAIL <-sp::merge(nypp_m, FAIL, by = "Precinct")

tm4<-tm_shape(ny_FAIL) + layout +
        tm_borders()+
        tm_fill("tot", palette=palb,
                title = "Fail to do sth") 

```


```{r}

MISSING<-viogroup%>%
        rename(Precinct=violation_precinct)%>%
        filter(Precinct<40, newg =="MISSING")%>%
        group_by(Precinct)%>%
        summarise(tot = n())

ny_MISSING <-sp::merge(nypp_m, MISSING, by = "Precinct")

tm5<-tm_shape(ny_MISSING) + layout +
        tm_borders()+
        tm_fill("tot", palette=palp,
                title = "Missing sth") 


```


```{r}

PARKING<-viogroup%>%
        rename(Precinct=violation_precinct)%>%
        filter(Precinct<40, newg =="NO PARKING")%>%
        group_by(Precinct)%>%
        summarise(tot = n())

ny_PARKING <-sp::merge(nypp_m, PARKING, by = "Precinct")

tm6<-tm_shape(ny_PARKING) + layout +
        tm_borders()+
        tm_fill("tot", palette=paly,
                title = "No Parking") 



STAND<-viogroup%>%
        rename(Precinct=violation_precinct)%>%
        filter(Precinct<40, newg =="NO_STAND")%>%
        group_by(Precinct)%>%
        summarise(tot = n())

ny_STAND <-sp::merge(nypp_m, STAND, by = "Precinct")

palyg <- RColorBrewer::brewer.pal(6,'YlGn')

tm7<-tm_shape(ny_STAND) + layout +
        tm_borders()+
        tm_fill("tot", palette=palyg,
                title = "No Stand") 




```

Four main groups: 

- NO STAND

- NO PARKING

- MISSING  

- FAIL TO

```{r}
tmap_arrange(tm4, tm5, asp = 1)
tmap_arrange(tm6, tm7, asp = 1)
```


# 3. Use geo-coding API to locate address for mapping

## a) Geocode at least 500 addresses of violations 

500 Violations on Ignoring Fire Hydrants


```{r, message=FALSE, warning=FALSE}
upper_east <- data%>%filter(violation_precinct==19 & violation_code==40)
        
library(ggmap)
upper_east500 <-upper_east%>%select(street_name, 
                              house_number,
                              vehicle_make,
                              issue_date)%>%
        mutate(address = paste(street_name, house_number, 
                               "New York, NY"))%>%
        select(-house_number)%>%
        sample_n(500)

my_key = readLines("~/.Renviron")
register_google(key = my_key)
upper_east500<-upper_east500%>%mutate_geocode(address)

```

Include a data table of these addresses and 
the latitude and longitude of these addresses in the output.
```{r}
adtable<-upper_east500%>%select(address,lat, lon)
adtable
```

# Interactive map with hover-over information
Provide an interactive map of the violations you geocoded using leaflet. Provide at least three pieces of information on the parking ticket in a popup.
```{r message=FALSE}
library(leaflet)
m<-leaflet(upper_east500) %>%  
  addTiles() %>%   
  addCircles(lng = ~lon, lat = ~lat)



content <- paste("Location:",upper_east500$street_name,"<br/>",
                 "Vehicle Brand:",upper_east500$vehicle_make,"<br/>",
                 "Date:",upper_east500$issue_date,"<br/>")

m %>% addCircles(popup = content) %>%
        setView(-73.95422, 40.77517,
                zoom = 14)
```

## c) Luxury Cars and Repeat Offenders
Using the vehicle Plate ID, identify repeat offenders (in the full data set). 
```{r}
repeat_off <-data%>%mutate(
        repeat_f = ifelse(duplicated(plate_id)==T, "Yes", "No"),
        luxury_c = ifelse(vehicle_make %in% c('BMW',
                                              'FERRA', 
                                              'ROLLS',
                                              'PORSC',
                                              'BENTL',
                                              'JAGUA',
                                              'LEXUS'), "Yes", "No"))%>%
        filter(violation_precinct==19 & violation_code==40)%>%
        select(street_name, house_number,vehicle_make,issue_date,
               repeat_f,luxury_c)%>%
        mutate(address = paste(street_name, house_number, 
                               "New York, NY"))%>%
        select(-house_number)%>%
        sample_n(500)
        
      
```

Start with the previous map. Distinguish the points by whether the car is a repeat offender and/or luxury car. Add a legend informing the user about the color scheme. 


```{r, message=FALSE, warning=FALSE}
repeat_off<-repeat_off%>%mutate_geocode(address)
```

Also make sure that the added information about the car type and repeat offender status is now contained in the pop-up information.
```{r}

r<-leaflet(repeat_off) %>%  
  addTiles() %>%   
  addCircles(lng = ~lon, lat = ~lat)



content_r <- paste("Location:",repeat_off$street_name,"<br/>",
                 "Vehicle Brand:",repeat_off$vehicle_make,"<br/>",
                 "Date:",repeat_off$issue_date,"<br/>",
                 "Luxury Car:", repeat_off$luxury_c,"<br/>")

library(RColorBrewer)
pal = colorFactor("Set1", domain =repeat_off$repeat_f)
color_offsel1 = pal(repeat_off$repeat_f)



r %>% addCircles(color = color_offsel1,  popup = content_r) %>%
  addLegend(pal = pal, values = ~repeat_off$repeat_f, 
            title = "Repeated Offender")%>%
        setView(-73.95422, 40.77517, zoom = 14)



```

# Interactive map with clustering
```{r}
r%>%addCircleMarkers(color = color_offsel1, 
                       popup = content,
                       clusterOptions = markerClusterOptions())%>%
        addLegend(pal = pal, values = ~repeat_off$repeat_f, 
            title = "Repeated Offender")%>%
        setView(-73.95422, 40.77517, zoom = 15)

```

